Manifold Destiny - or how to rig an election

### 2023-12-27 index.qmd
makefile
beff

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**

![](pngs/md.png)

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("dplyr")
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
```

```{webr-r}
ballcastsim <- function(
	dfm=app0,
	probw=c(0.5,0), 	
	probva=c(0.7,0.2,0.03,0.00), 				
	probvb=c(0.7,0.2,0.03,0.00), 
	ztech=c(0,0)
			){

  # Simulate prob
  probvrnd <<- dfm |>
    dplyr::mutate(ZV=rnorm(dplyr::n(),probw[1],probw[2])) |>
    dplyr::mutate(N=runif(dplyr::n(),ztech[1],ztech[2])) |>
    dplyr::mutate(p3=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probva[1],probva[3]))))) |>
    dplyr::mutate(p6=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probvb[1],probvb[3]))))) |>
    dplyr::mutate(p2=(1-p3)*pmax(0, pmin(1,rnorm(dplyr::n(),probva[2],probva[4])))) |>
    dplyr::mutate(p5=(1-p6)*pmax(0, pmin(1,rnorm(dplyr::n(),probvb[2],probvb[4])))) |>
    dplyr::mutate(p1=1-p2-p3) |>
    dplyr::mutate(p4=1-p5-p6) |>
    dplyr::select(P,ZV,N,p1,p2,p3,p4,p5,p6)

  #ballcodf <- dfm |> dplyr::left_join(probvrnd,by='P') |> base::split(.$P) |>
  #     purrr::map(function(x){
  ## Assigning voters in each precinct
  #cp <- stats::rbinom(x$R,1,x$ZV) 
  ### Setting up vector frame
  #dc <- data.frame(P=x$P,ZV=x$ZV,R=x$R,C=cp,p1=x$p1,p2=x$p2,p3=x$p3,p4=x$p4,p5=x$p5,p6=x$p6) |>
  #  dplyr::mutate(Id=row_number()) |> 
  #  dplyr::relocate(Id,.before=P)  |>
  #  dplyr::group_by(Id) |> 
  #  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(p1,p2,p3)),sample(4:6,1,prob=c(p4,p5,p6)))) |>
  #  dplyr::ungroup() 
  #})  |>
  #dplyr::bind_rows(.) |>
  #dplyr::mutate(Id=row_number(P)) |> 
  #dplyr::relocate(Id,.before=P) |> 
  #dplyr::mutate(S=ifelse(V==1,1,0)) |> 
  #dplyr::mutate(T=ifelse(V==4,1,0)) |>  
  #dplyr::mutate(U=ifelse(V==2,1,0)) |>
  #dplyr::mutate(V=ifelse(V==5,1,0)) |>
  #dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
  #dplyr::select(c('P','R','S','T','U','V')) |>
  #dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
  #dplyr::distinct() |> 
  #dplyr::mutate(Z=sum(S+T+U+V)) |>
  #dplyr::ungroup() 
}
print(ballcastsim())
```

@@

>>>>

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("dplyr","purrr"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
```

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("dplyr","purrr"))
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw=c(0.5,0.02)
probva=c(0.7,0.2,0.03,0.00)
probvb=c(0.7,0.2,0.03,0.00)
ztech=c(0,0)
# Simulate prob
probvrnd <<- dfm |>
  dplyr::mutate(ZV=rnorm(dplyr::n(),probw[1],probw[2])) |>
  dplyr::mutate(N=runif(dplyr::n(),ztech[1],ztech[2])) |>
  dplyr::mutate(p3=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probva[1],probva[3]))))) |>
  dplyr::mutate(p6=(1-ztech)*(1-pmax(0, pmin(1,rnorm(dplyr::n(),probvb[1],probvb[3]))))) |>
  dplyr::mutate(p2=(1-p3)*pmax(0, pmin(1,rnorm(dplyr::n(),probva[2],probva[4])))) |>
  dplyr::mutate(p5=(1-p6)*pmax(0, pmin(1,rnorm(dplyr::n(),probvb[2],probvb[4])))) |>
  dplyr::mutate(p1=1-p2-p3) |>
  dplyr::mutate(p4=1-p5-p6) |>
  dplyr::select(P,RV,ZV,N,p1,p2,p3,p4,p5,p6) |>
  dplyr::group_split(P)
abc <- lapply(seq(1,length(probvrnd)),function(x){
  inpv <- probvrnd[[x]]
  dfa <- data.frame(P=rep(inpv$P,inpv$RV),R=inpv$RV,C=stats::rbinom(inpv$RV,1,inpv$ZV)) |> 
  dplyr::mutate(Id=dplyr::row_number()) |>
  dplyr::group_by(Id) |>
  dplyr::mutate(V=ifelse(C==1,sample(1:3,1,prob=c(inpv$p1,inpv$p2,inpv$p3)),sample(4:6,1,prob=c(inpv$p4,inpv$p5,inpv$p6)))) |>
  dplyr::mutate(S=ifelse(V==1,1,0)) |> 
  dplyr::mutate(T=ifelse(V==4,1,0)) |>  
  dplyr::mutate(U=ifelse(V==2,1,0)) |>
  dplyr::mutate(V=ifelse(V==5,1,0)) 
})
def <- do.call("rbind", abc) |> 
  dplyr::arrange(P) |>  dplyr::group_by(P)  |> 
  dplyr::select(c('P','R','S','T','U','V')) |>
  dplyr::mutate(S=sum(S),T=sum(T),U=sum(U),V=sum(V)) |>
  dplyr::distinct() |> 
  dplyr::mutate(Z=sum(S+T+U+V)) |>
  dplyr::ungroup() 
def
```

@@

```{r}
library(dplyr)

# Sample data frame
df <- data.frame(
  P = c(1, 2, 1, 2, 3),
  Value = c("A", "B", "C", "D", "E")
)

# Split the data frame by the 'P' column
df_list <- df %>% group_split(P)
str(df_list)
# Access the individual groups
for (group in df_list) {
  print(group)
}
```

### 2023-12-27 presentation.qmd
beff

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
```

>>>>

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
```
